Quality Control and Filtering

### 2021-04-21 functional_genomics/functional_genomics.Rmd
update

---
layout: default
title: "About"
nav_order: 1
---

@@

# Rigorous, Reproducible Research in Marine Genomics

Welcome! We are a working group dedicated to promoting reproducible and robust genomic research in marine science and evolutionary biology.

## Organizers:

Katherine Silliman and Sam Bogan

## Faculty Mentors

Jon Puritz and Andrew Whitehead

## Working group members

@@

setwd("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/about/")
KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/about/about.Rmd")

>>>>

---
layout: default
title: "Functional Genomics"
nav_order: 2
has_children: true
---

@@

# Functional Genomics

@@

setwd("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/functional_genomics/")
KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/functional_genomics/functional_genomics.Rmd")

### 2021-04-21 genome_assembly/genome_assembly.Rmd
update

---
layout: default
title: "Functional Genomics"
nav_order: 2
has_children: true
---

@@

# Functional Genomics

@@

setwd("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/functional_genomics/")
KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/functional_genomics/functional_genomics.Rmd")

>>>>

---
layout: default
title: "Genome Assembly"
nav_order: 3
has_children: true
---

@@

# Genome Assembly

@@

setwd("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/genome_assembly/")
KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/genome_assembly/genome_assembly.Rmd")

### 2021-04-21 population_genetics/high_coverage.Rmd
update

---
layout: default
title: "Genome Assembly"
nav_order: 3
has_children: true
---

@@

# Genome Assembly

@@

setwd("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/genome_assembly/")
KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/genome_assembly/genome_assembly.Rmd")

>>>>

---
layout: default
title: "High Coverage"
parent: Whole Genome Sequencing
has_children: true
---

@@

# High Coverage WGS

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/high_coverage.Rmd")

### 2021-04-21 population_genetics/low_coverage.Rmd
update

---
layout: default
title: "High Coverage"
parent: Whole Genome Sequencing
has_children: true
---

@@

# High Coverage WGS

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/high_coverage.Rmd")

>>>>

---
layout: default
title: "Low Coverage"
parent: Whole Genome Sequencing
grand_parent: Population Genetics
has_children: true
---

@@

# Low Coverage

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/low_coverage.Rmd")

### 2021-04-21 population_genetics/population_genetics.Rmd
update

---
layout: default
title: "Low Coverage"
parent: Whole Genome Sequencing
grand_parent: Population Genetics
has_children: true
---

@@

# Low Coverage

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/low_coverage.Rmd")

>>>>

---
layout: default
title: "Population Genetics"
nav_order: 4
has_children: true
---

@@

# Population Genetics

Check out [Quality Control and Filtering](https://marineomics.github.io/Template_Site_1/Quality_Control_and_Filtering.html)

General introduction to whole genome sequencing and reduced representation sequencing. Pros and Cons for each.

@@

setwd("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/")
KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/population_genetics.Rmd")

### 2021-04-21 population_genetics/reduced_representation.Rmd
update

---
layout: default
title: "Population Genetics"
nav_order: 4
has_children: true
---

@@

# Population Genetics

Check out [Quality Control and Filtering](https://marineomics.github.io/Template_Site_1/Quality_Control_and_Filtering.html)

General introduction to whole genome sequencing and reduced representation sequencing. Pros and Cons for each.

@@

setwd("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/")
KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/population_genetics.Rmd")

>>>>

---
layout: default
title: "Reduced Representation"
parent: Population Genetics
has_children: true
---

@@

# Reduced Representation Sequencing

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/reduced_representation.Rmd")

### 2021-04-21 population_genetics/whole_genome_seq.Rmd
update

---
layout: default
title: "Reduced Representation"
parent: Population Genetics
has_children: true
---

@@

# Reduced Representation Sequencing

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/reduced_representation.Rmd")

>>>>

---
layout: default
title: "Whole Genome Sequencing"
parent: Population Genetics
has_children: true
---

@@

# Whole Genome Sequencing

Description of low vs. high coverage

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/whole_genome_seq.Rmd")

### 2021-04-21 quality_control/high_coverage.Rmd
update

---
layout: default
title: "Whole Genome Sequencing"
parent: Population Genetics
has_children: true
---

@@

# Whole Genome Sequencing

Description of low vs. high coverage

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/whole_genome_seq.Rmd")

>>>>

---
layout: default
title: "High Coverage"
parent: Quality Control and Filtering
has_children: true
---

@@

# High Coverage WGS Sequencing

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/quality_control/high_coverage.Rmd")

### 2021-04-21 quality_control/low_coverage.Rmd
update

---
layout: default
title: "Low Coverage"
parent: Whole Genome Sequencing
grand_parent: Population Genetics
has_children: true
---

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/population_genetics/low_coverage.Rmd")

>>>>

---
layout: default
title: "Low Coverage"
parent: Quality Control and Filtering
has_children: true
---

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/quality_control/low_coverage.Rmd")

### 2021-04-21 quality_control/quality_control.Rmd
update

---
layout: default
title: "Low Coverage"
parent: Quality Control and Filtering
has_children: true
---

@@

# Low Coverage

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/quality_control/low_coverage.Rmd")

>>>>

---
layout: default
title: "Quality Control and Filtering"
nav_order: 5
---

@@

# Quality Control and Filtering

Describe general considerations and link to `.fastq` to `.vcf` pipelines for specific -omics data types.

Describe common file formats?

@@

KnitPost("C:/Users/jmcgirr/Documents/GitHub/MarineOmics/Template_Site_1.github.io/quality_control/quality_control.Rmd")
